---
title: "Case Study Two"
author: "Julius Horvath, Michael Barker, Adam Scheerer"
date: "December 4, 2018"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1 

We will delete the Question 1 title above. Here are the questions we need to knock out. Remember this is not supposed to look like a student project so we will delete many of these things as they are completed.

a.	The client wants this to be reproducible and know exactly what you did.  There needs to be an informative Readme, complete with several sections, as referenced in Live Session.  Give contact information, session Info, and the objective of the repo at least.  

c.	Create a file structure that is accessible and transparent.  Document it in the root directory, ideally in the Readme.

```{r 1A, echo=TRUE}
sessionInfo()
```


```{r 2A, echo=TRUE}
data<-read.csv(file="CaseStudy2data.csv", header=TRUE)
print('The number of rows and columns in the data set are:')
nrow(data)
ncol(data)
```


## Cleaning the Data
```{r 2B, echo=TRUE}
data<-read.csv(file="CaseStudy2data.csv", header=TRUE)
names(data)
newnames<-read.csv("NewParameterNames.csv")
names(data)<-newnames$NewTerm
data$EmployeeCnt<- NULL
data$EmployeeNum<-NULL
data$StndHrs<-NULL
data$Over18<-NULL
data$Attrition<-as.character(data$Attrition)
data$Attrition[data$Attrition=='Yes']<-1
data$Attrition[data$Attrition=='No']<-0
data$JobRole<-as.character(data$JobRole)
data$JobRole[data$JobRole=='Human Resources']<-'HumanResources'
data$JobRole[data$JobRole=='Laboratory Technician']<- 'LabTech'
data$JobRole[data$JobRole=='Manager']<-'Manager'
data$JobRole[data$JobRole=='Manufacturing Director']<-'ManufacturingDirector'
data$JobRole[data$JobRole=='Research Director']<- 'ResearchDirector'
data$JobRole[data$JobRole=='Research Scientist ']<- 'ResearchScientist'
data$JobRole[data$JobRole=='Sales Executive']<-'SalesExecutive'
data$JobRole[data$JobRole=='Sales Representative']<- 'SalesRep'
data$OverTime<-as.character(data$OverTime)
data$OverTime[data$OverTime=='Yes']<-1
data$OverTime[data$OverTime=='No']<-0
data$MaritalStat <- as.character(data$MaritalStat)
data$MaritalStat[data$MaritalStat=='Married']<-1
data$MaritalStat[data$MaritalStat=='Single']<-0
data$MaritalStat[data$MaritalStat=='Divorced']<-2
data$Attrition<-as.integer(data$Attrition)
```
```{r 2D, echo=TRUE}
sapply(data, class) #this shows what class they are
```

## Checking to make sure the ages of our datapoints are appropriate...
```{r 3A, echo=TRUE}
min(data$Age) #checking to see if any under 18. Since there are not, no need to remove at this point. 
```
#### The data is appropriate to use, now we can begin our Exploratory Data Analysis
#### We have many histograms here for you to look at
```{r 3B, echo=TRUE}
data$LifeSat <- data$JobSat
data$LifeSat<- data$LifeSat +data$EnviroSat
data$LifeSat <- data$LifeSat+data$RelationSat
summary(data$JobSat)   #lets make these histograms look better and supply commentary on them.
hist(data$JobSat,main='Histogram of Job Satisfaction',xlab='Job Satisfaction',col='green',breaks=c(0,1,2,3,4),prob=T,ylim=c(0,0.35))
summary(data$YrsAtComp)   #How many years the employee was at the company.
hist(data$YrsAtComp,main='Histogram of Years at the Company',xlab='Years at Company',col='red',xlim=c(0,40),prob=T)
summary(data$Education)   #Education level of the employee. Each number indicates how many years of college they have completed.
hist(data$Education,main='Histogram of Education',xlab='Years of College completed',col='blue',xlim=c(1,5),breaks=c(0,1,2,3,4,5),prob=T)
summary(data$JobLevel)
hist(data$JobLevel,main='Histogram of Joblevel',xlab='Job Level', col='yellow',xlim=c(1,5))
summary(data$HourlyRate)   #The hourly rate of pay for the employee
hist(data$HourlyRate,main='Histogram of Hourly Rates',xlab='Dollars per Hour',col='DarkGreen',ylim=c(0,150))
summary(data$MonthlyRate)   #The monthly rate of pay (to display monthly income in comparison to hourly pay to show if the employee is less than or more than full time if hourly)
hist(data$MonthlyRate,main='Histogram of Monthly Rates',xlab='Dollars per Month', col='DarkBlue',xlim=c(2000,27000))
data$LifeSat <- data$JobSat
data$LifeSat<- data$LifeSat +data$EnviroSat
data$LifeSat <- data$LifeSat+data$RelationSat
hist(data$LifeSat,main='Histogram of Life Satisfaction',xlab='Life Satisfaction Metric', col='Purple',xlim=c(3,12),probability = T)
summary(data$LifeSat)  #Here is the Histogram of the metric we created for Life Satisfaction.  The Life Satisfaction score is simply the sum of Job Satisfaction, Environment Satisfaction, and Relationsip Satisfaction 
```
## Counts of relevant categories of data
```{r 3C, echo=TRUE}
summary(data$Gender)
table(data$Gender) #Counts of each gender.
summary(data$Education)
table(data$Education)#Counts of Education Level
summary(data$JobRole)
table(data$JobRole) #counts of each job role
```


```{r 3D, echo=TRUE}
table(data$JobRole)[4]  #This displays the number of managers in our dataset.
```
##Here are our barcharts that seperate a few relevant pieces of data by groups such as Job level and Job Role
```{r 4B, echo=TRUE}
library(ggplot2)
library(plyr)
data.to.plot <-ddply(data,.(JobLevel),summarize,MthlyInc = mean(MthlyInc))
data.to.plot$MthlyInc<- as.integer(data.to.plot$MthlyInc)
data.to.plot$JobLevel<-as.character(data.to.plot$JobLevel)
Income.by.joblevel <- ggplot(data=data.to.plot,aes(x=JobLevel,y=MthlyInc))+
  geom_bar(stat='identity',width=0.8,color='gold',fill='darkgreen')+
  theme_minimal()+
  coord_flip()+
  geom_text(aes(label=MthlyInc),color='white',hjust=1)+
  theme_minimal()+
  labs(title='Mean Monthly Income by Job Level',y='Mean Monthly Income',x='Job Level',caption='With data from DDSAnalytics')
Income.by.joblevel

Mean.tot.wrk.yrs.by.joblevel <- ddply(data,.(JobLevel),summarize,TotWrkYrs=mean(TotWrkYrs))
Mean.tot.wrk.yrs.by.joblevel$JobLevel<-as.character(Mean.tot.wrk.yrs.by.joblevel$JobLevel)
Mean.tot.wrk.yrs.by.joblevel$TotWrkYrs<- as.integer(Mean.tot.wrk.yrs.by.joblevel$TotWrkYrs)
Wrk.yrs.joblevel.plot <-ggplot(data=Mean.tot.wrk.yrs.by.joblevel,aes(x=JobLevel,y=TotWrkYrs))+
  geom_bar(stat='identity', width=0.8,color='red',fill='darkblue')+
  theme_minimal()+
  coord_flip()+
  geom_text(aes(label=TotWrkYrs),color='white',hjust=2)+
  theme_minimal()+
  labs(title='Mean Total Work Years by Job Level',y='Mean Total Work Hours',x='Job Level',caption='With data from DDSAnalytics')
summary(Wrk.yrs.joblevel.plot)
Wrk.yrs.joblevel.plot#This builds on the scatterplot in the next chunk that has log(Monthly Inc) plotted against Age and Years Worked.  The higher the job level correlates with more years worked and in turn high Monthly wages.
job.level.5 <- subset(data,JobLevel==5,select=c(JobLevel,Attrition))
count(job.level.5$Attrition,vars=1)#Here we see an Attrition rate of 7% at Job Level 5

job.level.3 <- subset(data,JobLevel==3,select=c(JobLevel,Attrition))
count(job.level.3$Attrition,vars=1) #Attrition rate rises to 14.7% at Job Level 3

job.level.1 <- subset(data,JobLevel==1,select=c(JobLevel,Attrition))
count(job.level.1$Attrition,vars=1) #Again the Attrition rate continues to rise and is up to 26.3% at Job Level 1
#We see in our final linear regression equation toward the end that each additional Work Year lowers the chance of attrition by 0.008 so all of this seems to add up.

LifeSat.by.JobRole <- ddply(data,.(JobRole),summarize,LifeSat=mean(LifeSat))
LifeSatPlot<- ggplot(data=LifeSat.by.JobRole,aes(x=reorder(JobRole,LifeSat),y=LifeSat))+
  geom_bar(stat='identity',width=0.8,color='steelblue',fill='white')+
  coord_flip()+
  theme_minimal()+
  geom_text(aes(label=LifeSat),color='black',hjust=2)+
  theme_minimal()+
  labs(title='Mean Life Satisfaction by Job Role',y='Mean Life Satisfaction',x='Job Role',caption='With data from DDSAnalytics')
LifeSatPlot #We can see that the mean Life Satisfaction is actually pretty similar across Job Roles however.  Indicating that it may not be what you do, but how long you've done it that decides your life satisfaction.

Job.role.best <- subset(data,JobRole=='ManufacturingDirector',select=c(JobRole,Attrition))
count(Job.role.best$Attrition,vars=1) #6.9% attrition for the most satisfied job

Job.role.worst <- subset(data, JobRole=='ResearchDirector',select=c(JobRole,Attrition))
count(Job.role.worst$Attrition,vars=1) #2.5% attrition for the least satisfied job although there may be sample size issues with this.







```

##Searching for a relationship between age and Income, followed by checking for differences amongst Gender
```{r 4C, echo=TRUE}
library(car)
Age.vs.Log.Mthly.Inc <- lm((log(data$MthlyInc))~data$Age)
plot(data$Age,log(data$MthlyInc),ylab='Log(Monthly Income)',xlab='Age',
     main='Log(Monthly Income) by Age')
abline(Age.vs.Log.Mthly.Inc,col='red')#log transform helps clarify the plots. There appears to be a relationship between age and monthly income, however age is really just a proxy for things like experience or time at a company/in the workforce. plotting those you get a much stronger relationship. 
plot(data$TotWrkYrs, log(data$MthlyInc),ylab='Log(Monthly Income)',xlab='Years Worked',main='Log(Monthly Income) vs Years Worked')
abline(lm((log(data$MthlyInc))~data$TotWrkYrs),col='blue')#You can see here that Years Worked has a similar trendline to Age.
plot(data$YrsAtComp, log(data$MthlyInc),ylab='Log(Monthly Income)',xlab='Years at Company',main='Log(Monthly Income) vs Years at Company')
abline(lm((log(data$MthlyInc))~data$YrsAtComp),col='green')#You can see again that Years at company and Years Worked are very similar in slope.
scatterplot(log(data$MthlyInc)~data$Age | data$Gender,data=data,regLine=T,
            xlab='Age',ylab='Log(Montly Income)',main='Age vs Log(Monthly Income)',legend=F)
legend(50, 7.5, legend=c('Male','Female'),col=c('blue','pink'),lty=1:1,box.col='black')
#It does not appear that either gender has a significant difference in the correlation between Age and the change in Monthly Income.

```


#Model Building time!!
```{r}
library(MASS)
library(tidyverse)
library(caret)
library(leaps)
head(data)
full.model <- lm(data$Attrition~.,data=data)
step.model <- stepAIC(full.model,direction = 'both')
summary(step.model)
models <- regsubsets(Attrition~.,data=data,nvmax=3,method='seqrep')
summary(models)
three.variable.model <- lm(Attrition~LifeSat+TotWrkYrs+OverTime,data=data)
summary(three.variable.model)  #Here is the summary of our 3 variables that contribute most to attrition, all very statistically significant
set.seed(123)
train.control<-trainControl(method='cv',number=10)
step.model<- train(Attrition~.,data=data,method='leapSeq',
                   tuneGrid=data.frame(nvmax=1:5),
                   trControl=train.control)
step.model$results
step.model$bestTune  #This tells us that our best model for predicting attrition has 4 variables.
summary(step.model$finalModel)
best.tune.model <-lm(Attrition~data$OverTime+data$StkOptLevel+data$TotWrkYrs+LifeSat,data=data)
summary(best.tune.model)#Here is our new model after using 10fold cross-validation to estimate prediction error
```
### We have given our two best models, the best 3 variable model is 
##### Attrition = 0.462-0.032*LifeSat-0.008*TotWrkYrs+0.214*OverTimeYes

### the best model however has 4 variables and is 
##### Attrition = 0.513 + 0.214*OverTimeYes -0.06*StkOptLevel - 0.008*TotWrkYrs -0.0334*LifeSat

#####All of the coefficients have significant t-values, their absolute values are all greater than 5 which you can see in our summary report.  These large t-statistics lead to very small probabilities that we would see this relationship between variables by chance.


```{r 4D, echo=TRUE}
plot(data$LifeSat)
scatterplot(log(data$MthlyInc)~log(data$LifeSat),data=data,regLine=T,
            xlab='log(Life Satisfaction)',ylab='log(Monthly Income)', main='Life Satisfaction vs Monthly Income')
#there does not appear to be a clear relationship between Life Satisfaction and Monthly Income 

```
##We cannot see a relationship between Life Satisfaction and Monthly Income, this relationship may be hidden within the groups of job roles and job levels and not life satisfaction.
